Mendelian randomization for causal inference in genome-wide association studies

### 2022-03-02 mr-review.Rmd
added sentences about 3 more methods

@van_der_graaf_mendelian_2020

>>>>

MR-link, reported by @van_der_graaf_mendelian_2020, aims to account for unobserved pleiotropy and 
linkage disequilibrium by using individual-level data on the outcome variable and summary statistics for the exposure. MR-link uses a three-step procedure to estimate causal effects.

1. Use GCTA-COJO to obtain SNP instruments [@genetic_investigation_of_anthropometric_traits_giant_consortium_conditional_2012]  
1. Prune all SNPs in linkage disequilibrium with the SNP instruments to obtain a set of "tag" SNPs 
with correlations less than 0.95  
1. Solve for the causal effect estimate with ridge regression of the outcome on the matrix resulting from concatenation of the SNP instrument genotypes matrix and the tag SNPs genotypes matrix.

Note that in step 3, ridge regression is preferred to ordinary least squares due to the limited 
statistical power of ordinary least squares in this setting. Presumably, this is due to collinearity in 
the matrix of tag SNP genotypes.

@jiang_hierarchical_2021, building on research from @newcombe2016jam, present a two-stage hierarchical Bayesian 
model that aims to unify MR and transcriptome-wide association studies frameworks.

Genetic instrumental variable regression uses GWAS summary statistics to construct polygenic scores for 
the outcome of interest [@diprete_genetic_2018]. In constructing polygenic scores from subsets of a GWAS 
cohort, @diprete_genetic_2018 aim to reduce bias due to horizontal pleiotropy.
